Biomass trends and figures

### 2019-08-09 analysis/VOCC/2-biomass-trends.Rmd
update variable name

current_biomass <- plot_vocc(out_mature,
    fill_col = "var_1_e",
    fill_label = "Mean mature \nbiomass (kg/ha)\npost-2010",
    raster_alpha = 1,
    viridis_option = "C",
    vec_aes = NULL,
    transform_col = fourth_root_power
  )
current_biomass <- current_biomass +
   geom_sf(data= trawl_footprint, aes(geometry=geometry/1000), colour = "gray", fill = "gray", alpha= 0.2, lwd=0.25, inherit.aes = FALSE) +
   coord_sf(xlim = c(180,820), ylim = c(5350,6050), datum = NULL) +
   xlab("") + 
   ylab("") +
   theme(panel.grid.major = element_line(colour = "transparent")) +
   ggtitle(paste("Predicted", species, "density with trawl footprint overlain"))
current_biomass
# }
```

>>>>

current_biomass <- plot_vocc(out_mature,
    fill_col = "est_exp_e",
    fill_label = "Mean mature \nbiomass (kg/ha)\npost-2010",
    raster_alpha = 1,
    viridis_option = "C",
    vec_aes = NULL,
    transform_col = fourth_root_power
  )
current_biomass <- current_biomass +
   geom_sf(data= trawl_footprint, aes(geometry=geometry/1000), colour = "gray", fill = "gray", alpha= 0.2, lwd=0.25, inherit.aes = FALSE) +
   coord_sf(xlim = c(180,820), ylim = c(5350,6050), datum = NULL) +
   xlab("") + 
   ylab("") +
   theme(panel.grid.major = element_line(colour = "transparent")) +
   ggtitle(paste("Predicted", species, "density with trawl footprint overlain"))
current_biomass
# }
```
